Jeff Goldsmith

### 2017-04-05 research.Rmd
new website; mostly complete with some chunks missing.

---
output:
  html_document:
    toc: true
    toc_float: true
---

@@

<br>
<font size="5">[Google Scholar Page](https://scholar.google.com/citations?user=3wvmkE0AAAAJ)</font> 
<br>

In the following, <sup>&#8224;</sup> denotes equal contribution and <sup>&#8225;</sup> indicates a student under my supervision.

## 2017

J. C. Cortes<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, J. Xu, N. Kim, A. R. Luft, P. Celnik, J. W. Krakauer, and T. Kitago (2017+).
A short and distinct time window for recovery of arm motor control after stroke revealed with a global measure of trajectory kinematics.
<i> Neurorehabilitation and Neural Repair, </i>
accepted.

M. Kronish, K. M. Diaz, **J. Goldsmith**, N. Moise, and J. E. Schwartz.
Objectively measured adherence to physical activity guidelines after acute coronary syndrome (2017+).
<i> Journal of the American College of Cardiology, </i>
accepted.

P. T. Reiss, **J. Goldsmith**, H. L. Shang, R. T. Ogden.
Methods for Scalar-on-Function Regression (2017+).
<i> International Statistical Review, </i>
accepted.

**J. Goldsmith**, J. E. Schwartz.
Variable Selection in the Functional Linear Concurrent Model (2017+).
<i> Statistics in Medicine, </i>
accepted.
[[PDF](Downloads/VBVS.pdf)
| [GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

J. Gertheiss, **J. Goldsmith**, H. L. Shang, A.-M. Staicu (2017).
A note on modeling sparse exponential-family functional response curves.
<i> Computational Statistics and Data Analysis, </i>
<b>105</b> 46-52.
[[Link](http://www.sciencedirect.com/science/article/pii/S0167947316301748) |
[GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

## 2016

A. Castano, M. Haq, D. Narotsky, **J. Goldsmith**, R. L. Weinberg, R. Morgenstern, T. Pozniakoff, F. L. Ruberg, E. J. Miller, J. L. Berk, A. Dispenzieri, M. Grogan, G.
Multicenter Experience of Planar Technetium Pyrophosphate Cardiac Imaging: Does Preferential Cardiac Uptake Predict Survival in Patients with ATTR Cardiac Amyloidosis?
<i> JAMA Cardiology, </i>
<b>1</b> 880-889.

**J. Goldsmith**.
vbvs.concurrent: Fitting Methods for the Functional Linear Concurrent Model (2016).
<i> The Journal of Open Source Software, </i>
<b>1</b>.
[[Link](http://joss.theoj.org/papers/a3884174f17dbb9a695f7b8658887eff) |
[GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

S. T. Sorge, D. C. Hesdorffer, J. C. Phelan, M. R. Winawer, S. Shostak, **J. Goldsmith**, W. K. Chung, R. Ottman (2016).
Genetic causal attribution and depression in multiplex epilepsy families.
<i> Epilepsia, </i>
<b>57</b> 1643-1650.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.13500/full)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27558297)]

A. L. Wong, **J. Goldsmith**, J Krakauer (2016).
A motor planning stage represents the shape of upcoming movement trajectories.
<i> Journal of Neurophysiolog, </i>
<b>116</b> 296-305.
[[Link](http://jn.physiology.org/content/116/2/296)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27098032)]

**J. Goldsmith**, X. Liu<sup>&#8225;</sup>, J. S. Jacobson, A. Rundle (2016).
New insights into activity patterns in children, found using functional data analyses.
<i> Medicine and Science in Sports and Exercise, </i>
<b>48</b> 1723-1729.
[[Link](http://journals.lww.com/acsm-msse/Abstract/2016/09000/New_Insights_into_Activity_Patterns_in_Children,.11.aspx)
| [PDF](Downloads/HeadStart.pdf)
| [Code](Downloads/HeadStartCode.zip)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27183122)]

J. Wrobel<sup>&#8225;</sup>, S.Y. Park, A.M. Staicu, **J. Goldsmith** (2016).
Interactive graphics for functional data analyses.
<i> Stat, </i>
<b>5</b> 108-118.
[[arXiv](http://arxiv.org/abs/1602.04091)
| [Link](http://onlinelibrary.wiley.com/doi/10.1002/sta4.109/abstract)
| [GitHub](https://github.com/refunders/refund.shiny)
| [CRAN](https://cran.r-project.org/web/packages/refund.shiny/index.html)]

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, T. Ogden (2016).
Variable Selection in Function-on-Scalar Regression.
<i> Stat, </i>
<b>5</b> 88-101.
[[Link](http://onlinelibrary.wiley.com/doi/10.1002/sta4.106/abstract)
| [PDF](Downloads/FoS_VarSelect.pdf)
| Implemented in [refund](https://github.com/refunders/refund) as fosr.vs()]

**J. Goldsmith**, T. Kitago (2016).
Assessing Systematic Effects of Stroke on Motor Control using Hierarchical Function-on-Scalar Regression.
<i> Journal of the Royal Statistical Society: Series C, </i>
<b>65</b> 215-236.
[[PDF](Downloads/BayesPFSR_Paper.pdf)
| [Link](http://onlinelibrary.wiley.com/doi/10.1111/rssc.12115/abstract)
| [Code](Downloads/BayesPFSR_Code.zip)
| [Shiny App](https://jeff-goldsmith.shinyapps.io/MotorControl_Interactive)]

C. B. Caminiti, D. C. Hesdorffer, S. Shostak, **J. Goldsmith**, S. T. Sorge, M. R. Winawer, J. C. Phelan, W. K. Chung, and R. Ottman (2016).
Parents' interest in genetic testing of their offspring in multiplex epilepsy families.
<i> Epilepsia, </i>
<b>57</b> 279-287.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.13287/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26693851)]

K. M. Diaz, D. J Krupka, M. J. Chang, J. A. Schaffer, Y. Ma, **J. Goldsmith**, J. E. Schwartz, K. W. Davidson (2016).
Validation of the Fitbit One for physical activity measurement at an upper torso attachment site.
<i> BMC Research Notes, </i>
<b>9</b> 213.
[[Link](http://bmcresnotes.biomedcentral.com/articles/10.1186/s13104-016-2020-8)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27068022)]

M. Abdalla, **J. Goldsmith**, P. Muntner, K. M. Diaz, K. Reynolds, J. E. Schwartz, D. Shimbo (2016).
Is Isolated Nocturnal Hypertension a Reproducible Phenotype?
<i> American Journal of Hypertension, </i>
<b>29</b> 33-38.
[[Link](http://ajh.oxfordjournals.org/content/29/1/33.full.pdf+html)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25904648)]

## 2015

T. Kitago<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, L. Kane, J. Berard, S. Huang, S. Ryan, P. Mazzoni, J, Krakauer, and V. Huang (2015).
Robotic therapy for chronic stroke: general recovery of impairment or improved task-specific skill?
<i> Journal of Neurophysiology, </i>
<b>114</b> 1885-1894.
[[Link](http://jn.physiology.org/content/early/2015/07/10/jn.00336.2015.abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26032276)]
(&#8224; denotes equal contribution)

**J. Goldsmith**, V. Zipunnikov, J. Schrack (2015).
Generalized Multilevel Functional-on-Scalar Regression and Principal Component Analysis.
<i> Biometrics, </i>
<b>71</b> 344-353.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/biom.12278/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25620473)
| [Code](Downloads/GenMFPCA_Code.zip)
| [Shiny App](https://jeff-goldsmith.shinyapps.io/GFPCA_interactive)]

U. M. Schambra, **J. Goldsmith**, H. M. Schambra, K. Nunleya, S. Harirforoosh, Y. Liu , and S. S. Moy (2015).
Low and moderate prenatal ethanol exposure of mice during gastrulation or neurulation delays neurobehavioral development.
<i> Neurotoxicology and Teratology, </i>
<b>51</b> 1-11.
[[Link](http://www.sciencedirect.com/science/article/pii/S089203621530012X)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26171567)]

K. M. Diaz, D. J Krupka, M. J. Chang, J. Peacock, Y. Ma, **J. Goldsmith**, J. E. Schwartz, K. W. Davidson (2015).
Fitbit: An accurate and reliable device for wireless physical activity tracking.
<i> International Journal of Cardiology, </i>
<b>185</b> 138-140.
[[Link](http://www.internationaljournalofcardiology.com/article/S0167-5273(15)00276-4/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25795203)]

C. Wang, S. Vine, A. Hsiao, A. Rundle, and **J. Goldsmith** (2015).
Weight-Related Behaviors When Children are in School Versus on Summer Breaks: Does Income Matter?
<i> Journal of School Health, </i>
<b>85</b> 458-466.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/josh.12274/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26032276)]

M. Sabatello, J. Phelan, D. C. Hesdorffer, S. Shostak, **J. Goldsmith**, S. Sorge, M. Winawer, W. Chung, R. Ottman (2015).
Genetic Causal Attribution of Epilepsy and its Implications for Felt Stigma.
<i> Epilepsia, </i>
<b>56</b> 1542-1550.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.13113/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26290354)]

## 2014

**J. Goldsmith**, L. Huang, C. M. Crainiceanu (2014).
Smooth Scalar-on-Image Regression via Spatial Bayesian Variable Selection.
<i> Journal of Computational and Graphical Statistics, </i>
<b>23</b> 46-64.
[[Link](http://amstat.tandfonline.com/doi/abs/10.1080/10618600.2012.743437#.U2pt-17A7d4) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24729670)]

**J. Goldsmith**, F. Scheipl (2014).
Estimator Selection and Combination in Scalar-on-Function Regression.
<i> Computational Statistics and Data Analysis, </i>
<b>70</b> 362-372.
[[Link](http://www.sciencedirect.com/science/article/pii/S0167947313003629) |
[PDF](Downloads/Ensembling_Paper.pdf) |
[Code](Downloads/Ensembling_Code.zip)]

J. A. Schrack, V. Zipunnikov, **J. Goldsmith**, K. Bandeen-Roche, C. M. Crainiceanu, L. Ferrucci (2014).
Estimating Energy Expenditure from Heart Rate in Older Adults: a Case for Calibration.
<i> PLoS One, </i>
<b>9</b> 1-9.
[[Link](http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0093520) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24787146)]

J. A. Schrack, V. Zipunnikov, **J. Goldsmith**, J. Bai, E. M. Simonsick, C. M. Crainiceanu, L. Ferrucci (2014).
Assessing the "Physical Cliff": Detailed Quantification of Aging and Physical Activity.
<i> Journal of Gerontology: Medical Sciences. </i>
<b>69</b> 973-979.
[[Link](http://biomedgerontology.oxfordjournals.org/content/69/8/973.full.pdf) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24336819) |
Article selected as "Editor's Choice"]

S. Vullaganti, **J. Goldsmith**, S. Teruya, J. Alvarez, S. Helmke, M. Maurer (2014).
Cardiovascular effects of hemoglobin response in patients receiving epoetin alfa and oral iron in heart failure with a preserved ejection fraction.
<i> Journal of Geriatric Cardiology, </i>
<b>11</b> 100-105.
[[Link](http://www.jgc301.com/ch/reader/view_abstract.aspx?file_no=20140227001&flag=1)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25009558)]

B. Swihart, **J. Goldsmith**, C. M. Crainiceanu. (2014).
Restricted Likelihood Ratio Tests for Functional Effects in the Functional Linear Model.
<i> Technometrics, </i>
<b>56</b> 483-493.
[[Link](http://www.tandfonline.com/doi/full/10.1080/00401706.2013.863163)]

A. Hauschild, S. C. Chen, M. Weichenthal, A. Blum, H. C. King, **J. Goldsmith**, D. O. Scharfstein, D. Gutkowicz-Krusin (2014).
To excise or not: impact of MelaFind on German dermatologists' decisions to biopsy atypical lesions.
<i>JDDG: Journal der Deutschen Dermatologischen Gesellschaft, </i>
<b>12</b> 606-614.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/ddg.12362/abstract) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24944011)]

J. O. Okeke, V. E. Tangel, S. T. Sorge, D. C. Hesdorffer, M. R. Winawer, **J. Goldsmith**, J. Phelan, W. Chung, S. Shostak, R. Ottman (2014).
Genetic Testing Preferences in Families Containing Multiple Individuals with Epilepsy.
<i>Epilepsia, </i>
<b>55</b> 1705-1713.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.12810/full) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25266816)]

G. S. Lovasi, **J. Goldsmith** (2014).
Invited commentary: Taking advantage of time-varying neighborhood environments.
<i>American Journal of Epidemiology, </i>
<b>DOI:</b> 10.1093/aje/kwu170.
[[Link](http://aje.oxfordjournals.org/content/180/5/462.full) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25117659)]

N. Cyrille, **J. Goldsmith**, J. Alvarez, M. S. Maurer (2014).
Prevalence and Prognostic Significance of Low QRS Voltage Among the Three Main Types of Cardiac Amyloid.
<i> American Journal of Cardiology, </i>
<b>114</b> 1089-1093.
[[Link](http://www.sciencedirect.com/science/article/pii/S0002914914014544#) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25212550)]

R. T. Shinohara, E. M. Sweeny, **J. Goldsmith**, N. Shiee, F. J. Mateen, P. A. Calabresi, S. Jarso, D. L. Pham, D. S. Reich, C. M. Crainiceanu (2014).
Statistical Normalization Techniques for Magnetic Resonance Imaging.
<i> NeuroImage: Clinical, </i>
<b>6</b> 9-19
[[Link](http://www.sciencedirect.com/science/article/pii/S221315821400117X#) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25379412)]

## 2013

**J. Goldsmith**, S. Greven, C. M. Crainiceanu (2013).
Corrected Confidence Bands for Functional Data Using Principal Components.
<i> Biometrics, </i>
<b>69</b> 41-51.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/j.1541-0420.2012.01808.x/abstract) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23003003)]

J. Gertheiss, **J. Goldsmith**, C. M. Crainiceanu, S. Greven. (2013).
Longitudinal Scalar-on-Functions Regression with Application to Tractography Data.
	<i> Biostatistics. </i>
<b>14</b> 447-461.
[[Link](http://biostatistics.oxfordjournals.org/content/14/3/447.long) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23292804)]

H. Sorensen, **J. Goldsmith**, L. Sangalli. (2013).
An Introduction with Medical Applications to Functional Data Analysis.
<i> Statistics in Medicine. </i>
<b>32</b> 5222-5240.
[[Link](http://www.tandfonline.com/doi/abs/10.1080/10618600.2012.679241) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23794794)]

L. Huang, **J. Goldsmith**, P. T. Reiss, D. S. Reich, C. M. Crainiceanu. (2013).
Bayesian Scalar-on-Image Regression with Application to Association Between Intracranial DTI and Cognitive Outcomes.
<i> NeuroImage. </i>
<b>83</b> 210-223.
[[Link](http://www.sciencedirect.com/science/article/pii/S1053811913006575) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23792220)]

F. J. Leyva, R. P. Bakshi, E. J. Fuchs, L. Li, B. S. Caffo, **J. Goldsmith**, Y. Du, J. P. Leal, L. A. Lee, M. S. Torbenson, C. W. Hendrix (2013).
Iso-osmolar enemas demonstrate preferential gastrointestinal distribution, safety, and acceptability compared with hyper- and hypo-osmolar enemas as a potential delive
<i> AIDS Research and Human Retroviruses. </i>
<b>29</b> 1487-1495.
[[Link](http://online.liebertpub.com/doi/abs/10.1089/aid.2013.0189) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23885722)]

## 2012

**J. Goldsmith**, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2012).
Longitudinal Penalized Functional Regression for Cognitive Outcomes on Neuronal Tract Measurements.
<i> Journal of the Royal Statistical Society: Series C, </i>
<b>61</b> 453-469.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/j.1467-9876.2011.01031.x/abstract) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22679339) |
[Simulation Code](Downloads/LPFR_Code.zip)]

T. Shinohara, **J. Goldsmith**, F. Mateen, D. S. Reich, C. M. Crainiceanu (2012).
Predicting Breakdown of the Blood-Brain Barrier in Multiple Sclerosis Without Contrast Agents.
<i> American Journal of Neuroradiology, </i>
<b>33</b> 1586-1590.
[[Link](http://www.ajnr.org/content/33/8/1586.long) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22442041)]

J. Bai, **J. Goldsmith**, B. S. Caffo, T. Glass, C. M. Crainiceanu (2012).
Movelets: A Dictionary of Movement.
<i> Electronic Journal of Statistics, </i>
<b>6</b> 559-578.
[[Link](https://projecteuclid.org/euclid.ejs/1334065322) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23293708)]

N. Louissant, S. Nimmagadda, R. Bakshi, Y. Du, K. Macura, K. King, R. Wahl, **J. Goldsmith**, B. S. Caffo,
Y.-J. Cao, J. Anderson, E. Fuchs, C. W. Hendrix (2012).
Distribution of Cell-free and Cell-associated HIV Surrogates in the Female Genital Tract following Simulated Vaginal Intercourse.
<i> Journal of Infectious Diseases, </i>
<b>205</b> 725-732.
[[Link](http://jid.oxfordjournals.org/content/205/5/725) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22279121)]

N. Louissant, S. Nimmagadda, E. Fuchs, R. Bakshi, Y. Cao, L. Lee, **J. Goldsmith**, B. S. Caffo, Y. Du, K. King,
F. Menendez, M. Torbenson, C. W. Hendrix (2012).
Distribution of Cell-free and Cell-associated HIV Surrogates in the Colon following Simulated Receptive Anal Intercourse.
<i> Journal of Acquired Immune Deficiency Syndromes, Basic and Translational Science, </i>
<b>59</b> 10-17.
[[Link](http://ovidsp.tx.ovid.com/sp-3.12.0b/ovidweb.cgi?&S=KOLDFPPIPMDDFJDMNCMKNBLBBJIDAA00&Link+Set=S.sh.27.28.32.42%7c2%7csl_10) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21937920)]

## 2011 and before

**J. Goldsmith**, J. Bobb, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2011).
Penalized Functional Regression.
<i> Journal of Computational and Graphical Statistics, </i>
<b>20</b> 830-851.
[[Link](http://www.tandfonline.com/doi/abs/10.1198/jcgs.2010.10007#.U1BzC16ft94) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22368438) |
[Simulation Code](Downloads/PFR_Code.zip)]

**J. Goldsmith**, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2011).
Penalized Functional Regression Analysis of White-Matter Tract Profiles in Multiple Sclerosis.
<i> NeuroImage, </i>
<b>57</b> 431-439.
[[Link](http://www.sciencedirect.com/science/article/pii/S1053811911004435) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21554962)]

**J. Goldsmith**, B. S. Caffo, C. M. Crainiceanu, D. Reich, Y. Du, C. W. Hendrix (2011).
Nonlinear Tube-Fitting for the Analysis of Anatomical and Functional Structures.
<i> Annals of Applied Statistics, </i>
<b>5</b> 337-363.
[[Link](http://projecteuclid.org/euclid.aoas/1300715193) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21709824)]

**J. Goldsmith**, M. P. Wand, and C. M. Crainiceanu (2011).
Functional Regression via Variational Bayes.
<i> Electronic Journal of Statistics, </i>
<b>5</b> 572-602.
[[Link](http://projecteuclid.org/euclid.ejs/1308143123) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22163061) |
[Simulation Code](Downloads/VB_Code.zip)]

C. M. Crainiceanu, **J. Goldsmith** (2010).
Bayesian Functional Data Analysis using WinBUGS.
<i> Journal of Statistical Software, </i>
<b>32</b> 1-33.
[[Link](http://www.jstatsoft.org/v32/i11/) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21743798)]

**J. Goldsmith**, L. Koss (2009).
Dynamical Properties of the Derivative of the Weierstrass Elliptic Function.
<i> Involve, </i>
<b>2</b> 267-288.
[[Link](http://msp.org/involve/2009/2-3/p02.xhtml) |
[pdf](Downloads/Weierstrass.pdf)]

>>>>

---
title: "Jeff Goldsmith"
---

@@

## Motion kinematics

(text placeholder)

## Wearable devices

(text placeholder)
